final figures for inclusion

### 2021-06-22 thesis writing/data_wrangling_plot.Rmd
reorganizing repo and creating data vis file for manuscript data analysis

```{r}
#with interaction term 
full_rf_model<-rma.mv(yi, vi, data=dat_MA_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level + resp_type, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_rf_model
```

```{r}
#plot to include to demonstrate model estimates
full_model_coefficients<- as.data.frame(coef(full_rf_model)) %>%
  tibble::rownames_to_column("covariates") %>%
  rename(value = "coef(full_rf_model)") %>%
  arrange(desc(value))

label.df <- data.frame(covariates = c("flux_range", "flux_range:mean_constant_temp", "org_level"),
                       value = c(0.3, -0.01, -0.69))

ggplot(data=full_model_coefficients, aes(x = reorder(covariates, value),
             y = value,
             fill = value > 0)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()+
  coord_flip()+
  geom_text(data=label.df, label = "*")

>>>>

```{r}
#with interaction term 
full_rf_model<-rma.mv(yi, vi, data=dat_MA_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level + resp_type, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_rf_model

#full model plus thermal stress
full_stress_model<-rma.mv(yi, vi, data=dat_MA_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level + resp_type + stressful, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_stress_model

```{r}
#plot to include to demonstrate model estimates
full_model_coefficients<- as.data.frame(coef(full_rf_model)) %>%
  tibble::rownames_to_column("covariates") %>%
  rename(value = "coef(full_rf_model)") %>%
  arrange(desc(value)) %>%
  mutate(coefficients = c("intercept", "response trait type", 
                          "fluctuation range", "mean temperature",
                          "fluctuation range:mean temperature",
                                       "size", "experimental age","organization level" 
                                      ))

label.df <- data.frame(coefficients = c("fluctuation range", "fluctuation range:mean temperature", "organization level"),
                       value = c(0.35, -0.07, -0.69))

ggplot(data=full_model_coefficients, aes(x = reorder(coefficients, value),
             y = value,
             fill = value > 0)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "Coefficient estimate") +
  scale_fill_viridis(discrete = TRUE)+
  theme_bw()+
  coord_flip()+
  geom_text(data=label.df, label = "*")

### 2021-06-22 thesis writing/thesis_draft/03-chap3.Rmd
reorganizing repo and creating data vis file for manuscript data analysis

The interaction between fluctuation range and mean temperature as well as fluctuation range is best displayed in Figure 3.3. At lower mean temperatures, higher fluctuation ranges generally have a more positive effect on organism responses and performance, though that trend starkly ends at about $24^{\circ}$C. However, at higher mean temperatures, lower fluctuation ranges appears to have an equally positive and negative effect on organism responses and performance (Figure 3.3).

```{r, echo=FALSE, message = FALSE, fig.cap="Scatterplot describing the relationship between mean temperature, temperature fluctuation range, and SMD. Temperature fluctuation ranged from 0-20°C, Mean temperature ranged from 7-33°C. SMD ranged from -4 to 6, restricted based on the distribution of SMD to minimize impact of outliers (see Appendix Figure 2).", fig.align="center", out.width = '90%', fig.scap="Scatterplot of relationship between range, mean, and SMD"}
normalized %>%
ggplot(aes(x=mean_temp_constant, y = yi, fill=flux_range))+
  geom_jitter(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")
```

@@

Equally as interesting as the significant model coefficients were the insignificant model coefficients: body size, thermal stress, life history traits, and experimental age. Body size has been identified as important in the allometric scaling of MTE and it is interesting that in these subsets of studies, body size did not explain the differences in responses across studies. This could simply be because we had a small sample size of studies (n=15), though multiple responses within each study contributed to a large sample of effect sizes (n=140), there were only a subset of relative body sizes included. It could also provide support for the argument against allometric scaling in MTE, such that there only individualized trends amongst taxonomic groups as opposed to general trends across individuals, populations, and communities of organisms [@clarke_scaling_1999; @clarke_temperature_2006]. This theory may also explain why thermal stress was not a significant predictor in our model, if MTE does not aptly describe the patterns that variability in temperature drives.

@@

We also expected for experimental age to be an important predictor, as the time period in which an organism experiences thermal variability has been demonstrated to be important for organisms like turtles, relying on TSD for development (Bowden and Paitz 2018). This may again be the result of studies not focused on the larval stage of development, but instead on the juvenile stage. However, there have been meta-analyses, both qualitative [@massey_measurement_2019], and quantitative [@noble_developmental_2018], that explicitly looked at the effects of incubation temperature on reptiles, concluding that there is a moderate to large effect of incubation temperature on the magnitude of response [@noble_developmental_2018]. These results align with patterns of juvenile organisms (e.g. fish) routinely having higher CTmax values than adults, such that life stage during experimental duration is of importance to thermal tolerance and performance [@portner_ecology_2008; @moyano_effects_2017].

>>>>

The interaction between fluctuation range and mean temperature as well as effect size is best displayed in Figure 3.3. At lower mean temperatures, higher fluctuation ranges generally have a more positive effect on organism responses and performance, though that trend starkly ends at about $24^{\circ}$C. However, at higher mean temperatures, lower fluctuation ranges appear to have an equally positive and negative effect on organism responses and performance (Figure 3.3).

```{r, echo=FALSE, message = FALSE, fig.cap="Scatterplot describing the relationship between mean temperature, temperature fluctuation range, and SMD. Temperature fluctuation ranged from 0-20°C, mean temperature ranged from 7-33°C. SMD ranged from -4 to 6, restricted based on the distribution of SMD to minimize impact of outliers (see Appendix Figure 2).", fig.align="center", out.width = '90%', fig.scap="Scatterplot of relationship between range, mean, and SMD"}
normalized %>%
ggplot(aes(x=mean_temp_constant, y = yi, fill=flux_range))+
  geom_jitter(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")
```

@@

Equally as interesting as the significant model coefficients were the insignificant model coefficients: body size, thermal stress, life history traits, and experimental age. Body size has been identified as important in the allometric scaling of MTE and it is interesting that in these subsets of studies, body size did not explain the differences in responses across studies. This could simply be because we had a small sample size of studies (n=15). Though multiple responses within each study contributed to a large sample of effect sizes (n=140), there were only a subset of relative body sizes included. It could also provide support for the argument against allometric scaling in MTE, such that there only individualized trends amongst taxonomic groups as opposed to general trends across individuals, populations, and communities of organisms [@clarke_scaling_1999; @clarke_temperature_2006]. This theory may also explain why thermal stress was not a significant predictor in our model, if MTE does not aptly describe the patterns that variability in temperature drives.

@@

We also expected for experimental age to be an important predictor, as the time period in which an organism experiences thermal variability has been demonstrated to be important for organisms like turtles, relying on TSD for development (Bowden and Paitz 2018). This may again be the result of studies not focused on the larval stage of development, but instead on the juvenile stage. However, there have been meta-analyses, both qualitative [@massey_measurement_2019], and quantitative [@noble_developmental_2018], that explicitly looked at the effects of incubation temperature on reptile development, concluding that there is a moderate to large effect of incubation temperature on the magnitude of response [@noble_developmental_2018]. These results align with patterns of juvenile organisms (e.g. fish) routinely having higher CTmax values than adults, such that life stage during experimental duration is of importance to thermal tolerance and performance [@portner_ecology_2008; @moyano_effects_2017].

### 2021-06-22 thesis writing/thesis_draft/05-appendix.Rmd
reorganizing repo and creating data vis file for manuscript data analysis

```{r, echo= FALSE}
table4 <- data.frame(Species = c("Drosophila melanogaster", "Leptopilina boulardi", 
                         "Mauremys reevesii", "Gryllus firmus", 
                         "Limnodynastes peronii", "Limnodynastes tasmaniensis", 
                         "Platyplectrum ornatum ", "Natrix natrix", 
                         "Coturnix japoncia", "Plestiodon chinensis", 
                         "Rhodnis prolixus", "Escherichia coli", 
                         "Salmonella", "Caiman latirostris", 
                         "Trachemys scripta", "Esteya vermicola", "Xylotrechus arvicola"), 
                 Topt = c("24-26.6°C", "25°C", "37.97 ± 0.64 °C", "30°C", "30°C", "30-33°C",
                          "33°C", "30°C", "26°C", "33°C", "30-35°C", "37°C, 35-36°C",
                          "35-36°C", "32-33°C", "32-33°C", "26°C", "N/A"), 
                 Class = c("Insecta", "Insecta", "Reptilia", "Insecta", "Amphibia", "Amphibia", "Amphibia",
                           "Reptilia", "Aves", "Reptilia", "Insecta", "Gammaproteobacteria",
                           "Gammaproteobacteria","Reptilia", "Reptilia", "Not assigned; Fungus", "Insecta"),
                 `Reference` = c("Klepsatel 2013, David 1988", "De lava et al 2016", 
                                 "Dang et al 2019", "Singh et al 2020", "Seebacher et al 2014",
                                 "Whitehead et al 1989", "Kern et al 2014", "Issac 1997",
                                 "Alagawany et al 2017", "Baojun et al 2010", "Fresquet and Lazzari 2011",
                                 "Doyle and Schoeni 1984, Bronikowski et al 2001", 
                                 "Bronikowski et al 2001", 
                                 "Simoncini et al 2019, Parachu-Marco et al 2017, Pina et al 2002", 
                                 "Dang et al 2019", "Wang et al 2015", "Garcia-Ruiz et al 2011"))
kable(table4, "latex", booktabs = T, 
      col.names = c("Species", "Topt (°C)", "Class", "Reference"), escape = F, caption = "TPC metrics extracted from additional papers to collect thermal history data for each species in the meta-analysis (missing data on species X. arvicola, used in Garcia-Ruiz et al 2011) and scientific classification at the class level", caption.short ="Thermal stress data by species") %>%
   row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
   kable_styling(latex_options = c("striped", "hold_position"))
```

>>>>

```{r, echo= FALSE}
table4 <- data.frame(Species = c("Drosophila melanogaster", "Leptopilina boulardi", 
                         "Mauremys reevesii", "Gryllus firmus", 
                         "Limnodynastes peronii", "Limnodynastes tasmaniensis", 
                         "Platyplectrum ornatum ", "Natrix natrix", 
                         "Coturnix japoncia", "Plestiodon chinensis", 
                         "Rhodnis prolixus", "Escherichia coli", 
                         "Salmonella", "Caiman latirostris", 
                         "Trachemys scripta", "Esteya vermicola", "Xylotrechus arvicola"), 
                 Topt = c("24-26.6°C", "25°C", "37.97 ± 0.64 °C", "30°C", "30°C", "30-33°C",
                          "33°C", "30°C", "26°C", "33°C", "30-35°C", "37°C, 35-36°C",
                          "35-36°C", "32-33°C", "32-33°C", "26°C", "N/A"), 
                 Class = c("Insecta", "Insecta", "Reptilia", "Insecta", "Amphibia", "Amphibia", "Amphibia",
                           "Reptilia", "Aves", "Reptilia", "Insecta", "Gammaproteobacteria",
                           "Gammaproteobacteria","Reptilia", "Reptilia", "Not assigned; Fungus", "Insecta"),
                 `Reference` = c("Klepsatel 2013, David 1988", "De lava et al 2016", 
                                 "Dang et al 2019", "Singh et al 2020", "Seebacher et al 2014",
                                 "Whitehead et al 1989", "Kern et al 2014", "Issac 1997",
                                 "Alagawany et al 2017", "Baojun et al 2010", "Fresquet and Lazzari 2011",
                                 "Doyle and Schoeni 1984, Bronikowski et al 2001", 
                                 "Bronikowski et al 2001", 
                                 "Simoncini et al 2019, Parachu-Marco et al 2017, Pina et al 2002", 
                                 "Dang et al 2019", "Wang et al 2015", "Garcia-Ruiz et al 2011"))
kable(table4, "latex", booktabs = T, 
      col.names = c("Species", "Topt (°C)", "Class", "Reference"), escape = F, caption = "TPC metrics extracted from additional papers to collect thermal history data for each species in the meta-analysis and scientific classification at the class level", caption.short ="Thermal stress data by species") %>%
   row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
   kable_styling(latex_options = c("striped", "hold_position"))
```
